COG-ED Manuscript

### 2021-08-17 06_Paper/COG-ED/Manuscript.Rmd
File import functional

>>>>

```{r libraries, echo=FALSE, message=FALSE, warning=FALSE}

  library(here)         # to set a directory without defined paths
  library(tidyverse)    # plotting and managing data

```

```{r import, echo=FALSE, message=FALSE, warning=FALSE}

  # set top level directory to source file

  here::i_am("Manuscript.Rmd")

  # import n-back and effort discounting data into a list each

  datalist_nback = lapply(list.files(here("Sampledata"), pattern = '.*nback.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)
  datalist_ED = lapply(list.files(here("Sampledata"), pattern = '.*ED.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)

  # put relevant data into a dataframe

```
